---
output:
  pdf_document: 
    keep_tex: true
  html_document: default
---
<!-- R Commander Markdown Template -->

Replace with Main Title
=======================

### mihap

### `r as.character(Sys.Date())`

```{r echo=FALSE}
# include this code chunk as-is to set options
knitr::opts_chunk$set(comment=NA, prompt=TRUE, out.width=750, fig.height=8, fig.width=8)
library(Rcmdr)
library(car)
library(RcmdrMisc)
```

```{r}
my.data <- 
  read.table("C:/Users/mihap/Code/Faks/famnit24-statistika/practice/data.txt",
   header=TRUE, stringsAsFactors=TRUE, sep="\t", na.strings="NA", dec=".", 
  strip.white=TRUE)
```


### Summarize Data Set: my.data
```{r}
summary(my.data)
```


```{r}
library(abind, pos=17)
```


```{r}
library(e1071, pos=18)
```



### Numerical Summaries: my.data

```{r}
Dataset <- 
  read.table("C:/Users/mihap/Code/Faks/famnit24-statistika/practice/data.txt",
   header=TRUE, stringsAsFactors=TRUE, sep="\t", na.strings="NA", dec=".", 
  strip.white=TRUE)
```


### Summarize Data Set: Dataset
```{r}
summary(Dataset)
```



### Histogram: Sport..hours.per.week.
```{r}
with(Dataset, Hist(Sport..hours.per.week., scale="frequency", 
  breaks="Sturges", col="darkgray"))
```


### Histogram: Sport..hours.per.week.
```{r}
with(Dataset, Hist(Sport..hours.per.week., scale="frequency", 
  breaks="Sturges", col="darkgray", xlab="Št. ur športa na teden", 
  ylab="Frekvenca"))
```


### Histogram: Sport..hours.per.week.
```{r}
with(Dataset, Hist(Sport..hours.per.week., scale="frequency", 
  breaks="Sturges", col="darkgray", xlab="Št. ur športa na teden", 
  ylab="Frekvenca"))
```

```{r}
with(Dataset, Hist(Sport..hours.per.week., scale="frequency",
breaks="Sturges", col="darkgray", xlab="Št. ur športa na teden",
ylab="Frekvenca"))
```



### Histogram: Sport..hours.per.week.
```{r}
with(Dataset, Hist(Sport..hours.per.week., groups=Smoking, 
  scale="frequency", breaks="Sturges", col="darkgray", 
  xlab="Št. ur športa na teden", ylab="Frekvenca"))
```


### Histogram: Weight
```{r}
with(Dataset, Hist(Weight, groups=Videogames, scale="frequency", 
  breaks="Sturges", col="darkgray"))
```


### Bar Plot: Videogames
```{r}
with(Dataset, Barplot(Videogames, by=Sex, style="divided", 
  legend.pos="above", xlab="Videogames", ylab="Frequency", label.bars=TRUE))
```


### Histogram: Weight
```{r}
with(Dataset, Hist(Weight, groups=Sex, scale="frequency", breaks="Sturges", 
  col="darkgray"))
```


### Histogram: Friends.on.Facebook
```{r}
with(Dataset, Hist(Friends.on.Facebook, groups=Videogames, 
  scale="frequency", breaks="Sturges", col="darkgray"))
```


### Bar Plot: Eye.Color
```{r}
with(Dataset, Barplot(Eye.Color, by=Sex, style="divided", 
  legend.pos="above", xlab="Eye.Color", ylab="Frequency", label.bars=TRUE))
```


### Bar Plot: Eye.Color
```{r}
with(Dataset, Barplot(Eye.Color, xlab="Eye.Color", ylab="Frequency", 
  label.bars=TRUE))
```

```{r}
library(colorspace, pos=19)
```



### Pie Chart: Eye.Color
```{r}
with(Dataset, piechart(Eye.Color, xlab="", ylab="", main="Eye.Color", 
  col=rainbow_hcl(5), scale="percent"))
```


### Pie Chart: Eye.Color
```{r}
with(Dataset, piechart(Eye.Color, xlab="", ylab="", main="Eye.Color", 
  col=palette()[2:6], scale="percent"))
```


### Pie Chart: Eye.Color
```{r}
with(Dataset, piechart(Eye.Color, xlab="", ylab="", main="Eye.Color", 
  col=palette()[2:6], scale="percent"))
```


### Bar Plot: Sex
```{r}
with(Dataset, Barplot(Sex, by=Faculty, style="divided", legend.pos="above", 
  xlab="Sex", ylab="Frequency", label.bars=TRUE))
```


### Scatterplot: Height~Weight
```{r}
scatterplot(Height~Weight, regLine=FALSE, smooth=FALSE, boxplots=FALSE, 
  data=Dataset)
```


### Scatterplot: Weight~Height
```{r}
scatterplot(Weight~Height, regLine=FALSE, smooth=FALSE, boxplots=FALSE, 
  data=Dataset)
```


### Numerical Summaries: Dataset
```{r}
numSummary(Dataset[,"Friends.on.Facebook", drop=FALSE], statistics=c("mean",
   "sd", "IQR", "quantiles"), quantiles=c(0,.25,.5,.75,1))
```


### Boxplot: ~ Friends.on.Facebook
```{r}
Boxplot( ~ Friends.on.Facebook, data=Dataset, id=list(method="y"))
```